TimeVaryingDetection_mrmr

### 2024-11-22 code/R/54188_ClassicCustomComparison_mrmr.Rmd
edit intro

```{r}
library(cmdstanr)
library(mrmr)
library(ggpubr)
library(dplyr)
```

@@

**Create a table comparing the mean generated quantity values for each model**

This table shows **only the mean** estimated value for each generated quantity. It is meant to serve as a quick reference for comparing model output. See the individual model summaries for complete generated quantity summaries.

```{r}
# pull quantities from model fit summary
N_classic <- classic_mod_54188_summary[4216:4220, 1:2]
N_custom <- custom_mod_54188_summary[4229:4233, 1:2]
B_classic <- classic_mod_54188_summary[4221:4225, 1:2]
B_custom <- custom_mod_54188_summary[4234:4238, 1:2]
Phi_classic <- classic_mod_54188_summary[4240:4243, 1:2]
Phi_custom <- custom_mod_54188_summary[4253:4256, 1:2]
p_classic <- classic_mod_54188_summary[4226:4239, 1:2]
p_custom <- custom_mod_54188_summary[4239:4252, 1:2]

@@

@@

```{r}
# visual comparison of abundance and recruitment plots
abund_recruit_comparison_plot_54188 <- ggarrange(classic_annotated, custom_annotated, ncol=2)
print(abund_recruit_comparison_plot_54188)
```

@@

-   LOO cross-validation uses log likelihood values, which now appear in the model summary as generated quantities, to evaluate how well the model predicts each data point when that point is left out of the fitting process. Likelihood, calculated at the individual level, is the probability of observing the data (in this case, an individual frog's capture history) given the model parameters.

@@

# calculate significance ratio
result <- elpd_diff_model1 / se_diff_model1

# interpret
if (abs(result) > 2) {
  cat("Result of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model fits the data significantly better than the classic model.\n")
} else {
  cat("Result of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model does not fit the data significantly better than the classic model.\n")
}

>>>>

```{r}
library(cmdstanr)
library(mrmr)
library(ggpubr)
library(dplyr)
library(gridExtra)
library(grid)
library(ggplot2)
```

@@

**Create a table comparing the mean and sd generated quantity values for each model**

This table shows **only the mean and sd** estimated value for each generated quantity. It is meant to serve as a quick reference for comparing model output. See the individual model summaries for complete generated quantity summaries.

```{r}
# pull quantities from model fit summary
N_classic <- classic_mod_54188_summary[4216:4220, c(1,2,4)]
N_custom <- custom_mod_54188_summary[4229:4233, c(1,2,4)]
B_classic <- classic_mod_54188_summary[4221:4225, c(1,2,4)]
B_custom <- custom_mod_54188_summary[4234:4238, c(1,2,4)]
Phi_classic <- classic_mod_54188_summary[4240:4243, c(1,2,4)]
Phi_custom <- custom_mod_54188_summary[4253:4256, c(1,2,4)]
p_classic <- classic_mod_54188_summary[4226:4239, c(1,2,4)]
p_custom <- custom_mod_54188_summary[4239:4252, c(1,2,4)]

@@

# Convert table to grob (graphical object)
table_grob <- tableGrob(GenQuant_comparison)

# Save as an image
ggsave("/Users/johnimperato/Desktop/Mossy-Pond/out/54188_comparison_table.png", plot = table_grob, width = 8, height = 8)

@@

```{r}
# visual comparison of abundance and recruitment plots
abund_recruit_comparison_plot_54188 <- ggarrange(classic_annotated, custom_annotated, ncol=2)
print(abund_recruit_comparison_plot_54188)

@@

-   LOO cross-validation uses log likelihood values, which now appear in the model summary as generated quantities, to evaluate how well the model predicts each data point when that point is left out of the fitting process. Likelihood, calculated at the individual level, is the probability of observing the data (in this case, an individual frog's capture history) given the model parameters. Log likelihood calculated at the individual level in the generated quantities block is different than the total log likelihood, summed across all individuals and sessions, calculated during model fitting in the model block.

@@

# calculate significance ratio
result <- abs(elpd_diff_model1 / se_diff_model1)

# interpret
if (abs(result) > 2) {
  cat("The absolute value of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model fits the data significantly better than the classic model.\n")
} else {
  cat("The absolute value of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model does not fit the data significantly better than the classic model.\n")
}
